SDR enhancement by clouds

### 2024-03-26 article/article.Rmd
Commit 2024-03-26 18:14

The shortwave solar irradiance, reaches the Earth's surface, is the main energy
source of the planet. It drives and governs the climate.
It has direct practical application, in different energy production method.  The
variability of its intensity, can cause difficulties in predicting the yield and
designing the appropriate equipment. An aspect of this variability are the
interaction

CE and ECE usefulness 
importance
problems

reported trends

CE mechanism

<!-- Define CE and ECE -->
In this study, we define as cloud enhancement events (CE) the cases when the measured
global horizontal irradiance (GHI) at ground level, exceeds the expected value under
clear-sky conditions.
Similar, we define the extreme cloud enhancement events (ECE), the cases when GHI,
exceeds the Total Solar Irradiance on horizontal plane at ground level.
Although the duration of these bursts varies from instantaneous to several minutes,
here we are constrained by the recorded data, to one-minute steps.

Identify CE cases

@@

Climatology and impact on the GHI

>>>>

The shortwave solar irradiance, reaches the Earth's surface, is the main energy
source of the planet. It drives and governs the climate.
It has direct practical application, in different energy production method.
.... cite ....
The variability of its intensity, can cause difficulties in predicting the yield and
designing the appropriate equipment.
.... cite ....
An aspect of this variability are the interaction with the clouds, where locally, under some
conditions the total shortwave irradiance reaching the ground can be higher than the
expected clear sky irradiance.
.... cite ....
Those enhancements have been reported to be able to exceed .... and duration.
.... cite ....

The underling mechanism of those events have been studied, with the main factor to be
.... cite ....

Methods of identification used
.... cite ....

...  reported trends ?...
.... cite ....

<!-- our work -->
In this study, we used modeled clear sky irradiance, in order to identify cloud
enhancement. We studied their occurrences, intensity and duration, in a thirty year
period at the city of Thessaloniki. We were able to determine some trends of the
phenomenon, it's Climatology, and some other statistical characteristics.

<!-- Define CE and ECE -->
here, we defined as cloud enhancement events (CE) the cases when the measured
global horizontal irradiance (GHI) at ground level, exceeds the expected value under
clear-sky conditions.
Similar, we defined as extreme cloud enhancement events (ECE), the cases when GHI,
exceeds the Total Solar Irradiance on horizontal plane at ground level.
Although the duration of these bursts varies, from instantaneous to several minutes,
here we are constrained by the recorded data, to one-minute steps.

@@
